When are Fuzzy Extractors Possible?

### 2014-09-18 info-bounds/FuzzyExtPossibility.tex
adding proof of ss hardness

\bnote{connection to obfuscation}
\section{Preliminaries}
\label{sec:preliminaries}
\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.  The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if the can guess $w\in W$ with noticeable probability.  More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.  This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.  Later, we will need this game to be zero sum.}

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ return $0$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

@@

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ return $0$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

The only difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.  In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.  These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{V}$ be a family of distributions.  Let $(\gen, \rep)$ be a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.  Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  Then there exists a fuzzy extractor $(\gen', \rep')$ is a $(\mathcal{M}, \mathcal{W}, \ell, t, \epsilon)$-fuzzy extractor.\footnote{Note the other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  We can think of the description of $W$ as side-information or leakage to the adversary.  The system designer, however never sees the particular outcome $W$.  This asymmetry will form the basis of our negative results in the next subsection.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{V}$ be a family of distributions.  Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  If there does not exist a $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor, then there is no $(\mathcal{M}, \mathcal{V}, \ell, t, \epsilon)$-fuzzy extractor.
\end{corollary}
%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for secure sketches as well as fuzzy extractors.  Additionally we elide the correctness term $\delta$ above, but these generalize the secure sketches and fuzzy extractors with imperfect completeness.

\subsection{Impossibility of info-theoretic sketches}
In the previous section, we saw that if a fuzzy extractor is secure for a family of sources, for every distribution over those sources there is a secure fuzzy extractor.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

\begin{theorem}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta \le 1/2$ for $\tilde{m} =\omega(1)$.  %Furthermore, consider $V$ as the uniform distribution over $\mathcal{V}$.  There is no secure sketch for $\mathcal{
\end{theorem}

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.  This type of distribution is a line in space $\mathbb{F}^\ell$.  Define $V$ as the uniform distribution over all such $W$.  Fix some $1< t < \ell$.
It suffices to show the following:

\begin{itemize}
\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$.
\item The distribution $V$ is uniform~(from the sketch designers point of view).
\item For any secure sketch on $V$, $H_0(V | \sketch(V)) \le n -\log |B_t|$.
\item The information $Z$ is a universal hash of $V$ that is independent of $\sketch(V)$. This suffices to show that $\Hav(V| \sketch(V), Z)$ is very small.
\end{itemize}
\begin{proposition} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some fixed $W\in\mathcal{V}$.  First note that since $w_1$ is uniform in a field of size $\omega(\poly(n))$, the distribution $\Hoo(W) =\omega(\log n)$.  Recall that $t< \ell$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \ell$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\ell$.
\end{proof}

\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\ell$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
\end{proof}
\bnote{will need to define average Hartley entropy}
\bnote{show version without error first?}
\begin{proposition}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $H_0(V | \sketch(V)) \le n - \log |B_t|+ O(1)$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{proposition}
\begin{proof}
By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w^*, \Pr_{p\leftarrow \sketch(w)} [\rec(w^*, p) = w] >1-\delta.
\]
By the Markov inequality, 
\[
\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
\]
That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.

Outline of what I want to say.
\begin{itemize}
\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
\end{itemize}
\end{proof}

\bnote{stopped here}
\end{proof}

\begin{lemma}
There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
\end{lemma}
\begin{proof}
Need to show several things.  
\begin{itemize}
\item Each component of the distribution has fuzzy min-entropy.
\item Any sketch must leak some information about $V$.
\item The side information can be thought of as a hash function.  Furthermore, it is independent of the sketch.  Thus, the sketch and hash are independent information.  Thus, conditioned on both there is almost no entropy.
\end{itemize}
\end{proof}

Canetti et al.~\cite[XXXX]{canetti2014key} construct computational fuzzy extractors for this family of distributions~(as long $\mathbb{F}$ is large enough).\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.

\begin{lemma}
There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
\end{lemma}

\begin{corollary}
This is also impossible for computational sketches that retain hill entropy.
\end{corollary}

\subsection{Conductors}
Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
\begin{lemma}
Not possible for information-theoretic objects.
\end{lemma}
\bibliographystyle{alpha}
\bibliography{crypto}

\appendix
\section{Block Unguessable Distributions}
\begin{definition}~\cite[Definition 4.2]{canetti2014key}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
\section{Leveraging convex combinations?}
\label{sec:convex comb}
In many situations solving a problem for min-entropy distributions can be reduced to solving the problem for flat distributions and then using the fact that any min-entropy distribution is a convex combination of flat distributions.  For example, consider the following hypothetical extension to \consref{cons:pairwise hash}.  Let $W$ be some distribution that is a finite convex combination of flat sources $W_1,..., W_n$ where each $\forall i, \Hoo(W_i)\ge k$.\footnote{A distribution may be an  convex combination of an infinite number of distributions.  However, the difficulty arises even when considering a finite combination so we restrict ourselves to this simpler case.}  For convenience we assume that the coefficients on all $W_i$ are the same and distributions may be repeated.

>>>>

\bnote{connection to obfuscation}
\section{Preliminaries}
\label{sec:preliminaries}
\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case version of this notion~(to the best of our understanding this has not been used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

@@

The security game of a fuzzy extractor can be thought of as a two stage process: 1) the challenger specifies $(\sketch, \rec)$, 2) the adversary specifies a source $W\in \mathcal{V}$.  The challenger wins if the adversary can guess the outcome of $W$ with low probability, and the adversary wins if they can guess $w\in W$ with noticeable probability.  More formally, let $\mathcal{A}, \mathcal{C}$ be the adversary and challenger respectively. We will formulate this as a two player game.\footnote{We denote the outcome of the game as a reward to each player.  This is opposed to the standard formulation saying that $\mathcal{A}$ wins or loses.  This is to apply results from game theory.}

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_1(\mathcal{A}, \mathcal{C}, k)$: \\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V})$\\
$W \leftarrow \mathcal{A}(\mathcal{V}, \sketch, \rec)$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

@@

\begin{center}
\begin{minipage}{1in}
\begin{tabbing}
123\=123\=123\=123\=123\=\kill
\textbf{Experiment} $\Exp^{\mathcal{V}}_2(\mathcal{A}, \mathcal{C})$: \\
$\mathcal{W} \leftarrow \mathcal{A}(\mathcal{V})$\\
$(\sketch, \rec)\leftarrow \mathcal{C}(\mathcal{V}, \mathcal{W})$\\
$W \leftarrow \mathcal{W}$\\
If $W\not\in \mathcal{V}$ reward $(1, -1)$.\\
If $\Hav(W | \sketch(W))\ge k$ set reward $(1, -1)$ else reward $(-1, 1)$.
\end{tabbing} \end{minipage} 
\end{center}

The difference between these two games is which player announces their action first, in $\Exp^{\mathcal{V}}_1$, the challenger announces a pair of algorithms, the adversary is then allowed to specify a source.  In $\Exp^{\mathcal{V}}_2$, the adversary specifies a distribution over sources, and the challenger then specifies their algorithm.  These two formulations are equivalent by the minimax theorem~\cite{neumann1928theorie}.

\begin{lemma}
\label{lem:quant switch fuzz}
Let $\mathcal{V}$ be a family of distributions.  Let $(\sketch, \rec)$ be a $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.  Then let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  Then there exists $(\sketch', \rec')$ that is a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-fuzzy extractor.\footnote{The other direction of this lemma is true as well.  If it is possible to construct a fuzzy extractor for an arbitrary distribution over a family then it is possible to construct a fuzzy extractor for every element of the family.}
\end{lemma}

Thus, instead of thinking of an adversary specifying a family of sources, we think of an adversary specifying a distribution over sources.  Importantly, the adversary sees the distribution $W$ and $\sketch(W)$ when they are trying to recover the particular outcome.  We can think of the description of $W$ as side-information or leakage to the adversary.  The system designer, however never sees the particular outcome $W$.  This asymmetry will form the basis of our negative results in the next subsection.

\begin{corollary}
\label{cor:no fuzz for dist}
Let $\mathcal{V}$ be a family of distributions.  Let $\mathcal{W}$ be an arbitrary distribution over elements of $\mathcal{V}$.  If there does not exist a $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch, then there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch.
\end{corollary}
%Ideally, a fuzzy extractor should work for any distribution~(or at least a large family of distributions).  However, as we show below the above construction does not extend to the setting of all well-spread distributions.  In the previous model the particular well-spread distribution $W$ was encoded in the \sketch and \rec algorithms.  In this section we ask if a similar construction is possible when $(\sketch, \rec)$ must work for any well-spread distribution.  In this setting, $(\sketch, \rec)$ are described and the adversary then specifies a particular well-spread distribution $W$.

@@

Both \lemref{lem:quant switch fuzz} and \corref{cor:no fuzz for dist} apply for fuzzy extractors as well as secure sketches.  Additionally they generalize to the case of imperfect correctness.

\subsection{Impossibility of info-theoretic sketches}
In the previous section, we saw that if a secure sketch is secure for a family of sources, for every distribution over those sources there is a secure sketch.  In this section, we will show there are distributions over families of distributions that do not admit a secure sketch.

\begin{theorem}
\label{thm:imposs sketch}
Let $n$ be a security parameter.  There exists a family of distributions $\mathcal{V}$ such that for each element $W\in \mathcal{V}$, $\Hfuzz(W)= \omega(\log n)$ and there is no $(\mathcal{M}, \mathcal{V}, \tilde{m}, t)$-secure sketch with error $\delta < 1/4$ for $\tilde{m} =\omega(1)$ for $t\ge 4$.  \bnote{finish proof}
\end{theorem}

@@

Let $\mathcal{V}$ be family of distributions of the form $W = w_1,..., w_\ell$ where $w_1$ is uniform and $w_i = a_i w_1 + b_i$ for $2\le i \le \ell$ and $a_i\neq 0$.  This type of distribution is an affine line in space $\mathbb{F}^\ell$.  Define $V$ as the uniform distribution over all such $W$.  Furthermore, the side information $Z = a_2, b_2, ..., a_\ell, b_\ell$. Fix some $4\le t < \ell$.
We then show the following:

\begin{itemize}
\item For all $W\in \mathcal{V}$, $\Hfuzz(W) = \omega (\log n)$. Alternatively, $\forall z, \Hfuzz(V | Z=z) = \omega(\log n)$.
\item The distribution $V$ is uniform~(from the sketch designers point of view).  That is $V\overset{d}=U$.
\item For any secure sketch on $V$, $\tilde{H}_0(V | \sketch(V)) \le  (\ell-t+1)\log |\mathbb{F}|+1$. 
\item Having seen $v\in V$, there are many possible values for $z_1, z_2$ for the side information $Z$~(and these possible values are equally likely).  Furthermore, the distributions $V|Z=z_1 $ and $V| Z=z_1$ have disjoint support outside of $v$.
\item For most values of possible $Z$ there are few values possible in the distribution $V | \sketch(V)$.  Thus, $\Hav(V| \sketch(V) , Z)$ is small.
\end{itemize}
\begin{proposition} 
\label{prop:each element good} For each $W\in\mathcal{V}$, $\Hfuzz(W) = \omega(\log n)$.
\end{proposition}
\begin{proof}
Consider some fixed $W\in\mathcal{V}$.  The value $w_1$ is uniform in a field of size $\omega(\poly(n))$, so $\Hoo(W) =\omega(\log n)$.  Recall that $t< \ell$.  We now show that for any $w, w'\in W$, $\dis(w, w') = \ell$ and thus $\Hfuzz(W) = \Hoo(W)$.  Fix some $w, w'\in W$.  Clearly, $w_1 \neq w_1'$, for any $i$, $w_i = a_i w_1 + b_i$ and $w_i' = a_i w_1' + b_i$.  Since $a_i\neq 0$, $a_iw_1 \neq a_iw_1'$ and thus $a_iw_1+b_i \neq a_iw_1'+b_i$.  That is, $\dis (w, w')  =\ell$.
\end{proof}

\begin{proposition}$V$ is the uniform distribution over $\mathbb{F}^\ell$.
\end{proposition}
\begin{proof}
Consider some $w\in V$.  Then $w$ was drawn from some intermediate distribution $W$ with coefficients $a_2, b_2, ..., a_\ell , b_\ell$.  The value $w_1$ is uniformly random and $w_i$ are uniformly random since $b_2,..., b_\ell$ are uniformly random.
\end{proof}
\begin{lemma}
Fix some $\sketch, \rec$ algorithm with error $\delta < 1/4$, then $\tilde{H}_0(V | \sketch(V)) \le (\ell-t+1)\log |\mathbb{F}|+1$.\footnote{This result is an extension of lower bounds from~\cite[Appendix C]{DBLP:journals/siamcomp/DodisORS08}.  Dealing with imperfect correctness makes the bound more complicated.  In particular, we can only argue about the average remaining support size.}
\end{lemma}
\begin{proof}
We assume that $\rec$ is deterministic in our analysis.  Any randomness necessary for the \rec algorithm can be provided by \sketch.  We will however, not consider these coins in our security analysis.

By the definition of correctness for $(\sketch, \rec)$, 
\[
\forall w, w', \Pr_{p\leftarrow \sketch(w)} [\rec(w', p) = w] >1-\delta.
\]
%For most $p$, $\rec$ works on most neighbors of $w$.  
Fix some $w$.  
By Markov's inequality, there exists a set $A_{ss}$ such that $\Pr[p\in A_{ss}]\ge 1/2$ and $\forall s\in A_{ss}$, 
\[
\{w' | \dis (w', w)\le t \wedge \rec(w', p) \neq w\}\le 2\delta < 1/2.\]

Consider some $p\in A_{ss}$.  We now show that $H_0(V | p) \le n-\log |B_t|$.  Note for the true value $w$ sketched $\{w' | \dis(w, w') \le t \wedge \rec(w', p) \neq w] \le 2\delta$.  Thus for every value in $V|p$ this is also true.  This makes the support of $V|p$ a $(t, 2\delta)$-Shannon code~(see \defref{def:shannon-code}).  In particular, this implies that for all $w_1, w_2 \in V|p$, $\dis(w_1, w_2)\ge t$~(since $2\delta< 1/2$).  That is $V|p$ is a set with minimum distance at least $t$.  By the Singleton bound, this implies that $H_0(V | p) \le (\ell -t+1 )|\mathbb{F}|$.  Averaging over $p$ one has that $\tilde{H}_0(V|P) \le (\ell -t +1) \log|\mathbb{F}| +1$.
%By the Markov inequality, 
%\[
%\forall w, w^*, \Pr_{p \leftarrow \sketch(w)} [ \Pr[\rec(w^*, p) = w] \le 1-2\delta ] < \delta /2.
%\]
%That is, for most $p$, $\Pr[\rec(w^*, p) = w] > 1-2\delta>1/2$.
%
%Outline of what I want to say.
%\begin{itemize}
%\item Suppose we are at some good sketch value, that is, the sketch decodes well for $w^*$ close to the true value $w$.
%\item Then for the true value that was sketched, for most neighbors $w^*$ of $w$, $\Pr[\rec(w^*, p) =w] >1/2$.  
%\item For a value $w'$ to be in the support of $W | P=p$, it must be for all neighbors of $\Pr[\rec( w', p) =w ]>1/2$.
%\item This implies that if $w_1, w_2 \in W|P = p$, then $\dis (w_1, w_2)\ge t$.
%\item Conditioned on $P=p$, $W| P=p$ is a good code for random errors.
%Consider some subset $G\subseteq supp(W| P=p)$ with $\Pr (W| P=p \in G)\ge 1/2$.  Then for all $w\in G$ the probability they recover correctly is at least $1-4\delta$~(by another application of Markov).  
%\item This, means that the size of $|G|$ is at most $n -\log |B_t|$.
%\end{itemize}
\end{proof}
We showed that for most values of $\sketch$ many values of $V$ are removed from the support.  We now show that the information contained in $Z$ is enough to nearly determine the actual sketched value.

\begin{lemma}
$\Hav(V | \sketch(V), Z) \le \Theta(1)$.
\end{lemma}
\begin{proof}
Recall that $Z$ consists of $2\ell$ coefficients and there are $(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}$ equally likely values for $Z$.
 By described above the view of $\sketch, \rec$ is a uniform distribution $V$.  We know show there are many possible values for $Z$.  The only information seen by $\sketch$ algorithm is in the point $V=v$.  The length of this point is $|\mathbb{F}|^\ell$.  Conditioned on this information there are still many possible values for $Z$.  That is, 
 \[
 \forall v, H_0(Z | V=v) =\log \left(\frac{(|\mathbb{F}|-1)^{\ell-1} |\mathbb{F}|^{\ell-1}}{|\mathbb{F}|^\ell}\right) = \log \left( (|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|\right).
 \]
Consider two possible $z_1, z_2$ that are possible values of $Z$.  The distributions $V| Z=z_1$ and $V | Z=z_2$ intersect at one point~(namely $v$).

This means that the $\sketch$ algorithm include points for possible $Z$ values~(other than $v$) and these values are disjoint.  The optimum strategy is to include these values uniformly from different $Z$ values.

We show this across different sketch values.  Consider some fixed sketch value $s$ and let $h_s \overset{def}= H_0(V | \sketch(V) = s)$.  That is, there are $2^{h_s}$ possible values for $V$ conditioned on $\sketch(V) = s$.  Furthermore, recall that 
\[
\log \expe_{s\in \sketch(V)} 2^{h_s} = \log \expe_{s\in \sketch(V)} 2^{H_0(V | \sketch(V) = s)}  = \tilde{H}_0(V | \sketch(V)) %\le   (\ell-t+1)\log |\mathbb{F}|+1.
\]  
Conditioned on seeing the point $V$ there are $(|\mathbb{F}|-1)^{\ell-1}/|\mathbb{F}|$ possible values for $Z$ with disjoint support outside of the sketched point.  Consider these possible values for $Z$ as bins to be filled with the $2^{h_s}$ balls~(possible values of $V | \sketch(V)=s$).  The average number of balls in each bin is maximized when the bins are filled equally.  That is, the average number of balls in each bin is bounded by the number of balls divided by the number of bins.  That is, 
\begin{align*}
\tilde{H}_0(V |Z  , \sketch(V) = s) &\le \log \left(\frac{\text{\# bins}}{\text{\# balls}}\right)\\
&= \log \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)
\end{align*}
\bnote{should I be writing this as $Z | \sketch(V) =s $?}
Then averaging over the possible values of $s$, we have the following:
\begin{align*}
\tilde{H}_0(V |Z , \sketch(V) ) &= \log \expe_{s\in \sketch(V)} 2^{\tilde{H}_0(V | Z, \sketch(V) =s )}\\
&= \log\expe_{s\in \sketch(V)} \left(\frac{2^{h_s}|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \right)\\
&= \log \frac{|\mathbb{F}|}{(|\mathbb{F}|-1)^{\ell-1}} \expe_{s\in \sketch(V)} 2^{h_s}\\
&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \log \expe_{s\in \sketch(V)} 2^{h_s}\\
&=\log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + \tilde{H}_0(V | \sketch(V))\\ 
&\le \log |\mathbb{F}| - (\ell -1)\log (|\mathbb{F}|-1) + (\ell-t+1)\log |\mathbb{F}|+1\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-1) \log (|\mathbb{F}|-1)+1\\
&\le (\ell-t+2)\log |\mathbb{F}| - (\ell-2) \log |\mathbb{F}|+1\\
&\le \Theta(1)
\end{align*}
 Where the last line follows for $t\ge 4$.  The eighth line follows from the seventh as long as $|\mathbb{F}|????$\bnote{fix this}
 \end{proof}

 \thref{thm:imposs sketch} follows using the change of quantifiers in \corref{cor:no fuzz for dist}.
%\begin{lemma}
%$\Hav(V| P , Z) = \Theta(1)$
%\end{lemma}
%\begin{proof}
%Consider some fixed $p$.
%If $Z$ is universal then $\forall w_1, w_2 \in V|P=p, w_1\neq w_2$\bnote{why should $Z$ be universal for the entire range, I get for each coordinate.}
%\[
%\Pr[Z(w_1) = Z(w_2)] = \frac{1}{|Z|}.
%\]
%Then by the union bound, 
%\[
%\Pr[\exists w_1\neq w_2 \wedge Z(w_1) = Z(w_2)]\le \frac{ 2^{H_0(V|P=p)}}{|Z|}.
%\]
%\bnote{need to average across $P$}
%\bnote{I'm confused about what we mean by $Z$ being universal here.}
%\bnote{working here!}
%\end{proof}
%
%\bnote{stopped here}
\end{proof}

%\begin{lemma}
%There does not exist a secure secure sketch for $V$ with super-logarithmic residual min-entropy.
%\end{lemma}
%\begin{proof}
%Need to show several things.  
%\begin{itemize}
%\item Each component of the distribution has fuzzy min-entropy.
%\item Any sketch must leak some information about $V$.
%\item The side information can be thought of as a hash function.  Furthermore, it is independent of the sketch.  Thus, the sketch and hash are independent information.  Thus, conditioned on both there is almost no entropy.
%\end{itemize}
%\end{proof}

Canetti et al.~\cite{canetti2014key} construct computational fuzzy extractors for this family of distributions when $\mathbb{F}$ is large enough.\bnote{fill in right theorem number}  This result presents a contrast between what is possible for sketches and fuzzy extraction.

%\begin{lemma}
%There is a family of distributions such that for any secure sketch that works for an adversarial choice of the distribution, there is no residual entropy conditioned on adversary knowledge and the secure sketch.
%\end{lemma}

\begin{corollary}
This is also impossible for computational sketches that retain hill entropy.\bnote{fill this in, use asiacrypt result.}
\end{corollary}

%\subsection{Conductors}
%Possible for computational objects.  See the constructions of Canetti et al.~\cite{canetti2014key}.
%\begin{lemma}
%Not possible for information-theoretic objects.
%\end{lemma}
\bibliographystyle{alpha}
\bibliography{crypto}

\appendix
\section{Coding Theory}
\begin{definition}
\label{def:shannon-code}
Let $\mathcal{C}$ be a set over space $\mathcal{M}$.  We say that $\mathcal{C}$ is an $(t,\epsilon)$-\emph{Shannon code} if there exists an efficient procedure $\rec$ such that for all $c\in \mathcal{C}$, $\Pr_{w' | \dis(w', w)\le t}[\rec(c') \neq c]\le \epsilon$. To distinguish it from the average-error Shannon code defined below, we will sometimes call it \emph{maximal-error} Shannon code.
\end{definition}

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\neigh(c, t')) \neq c]\le \epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} %(we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $\mathcal{C}'$ with $|\mathcal{C}'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}
